\chapter{Bibliografía}

\begin{thebibliography}{X}
\bibitem{1} \textsc{Van Vinh Nguyen} y \textsc{Weon Lee Jong}, <<Self-Positioning System for Indoor Navigation on Mobile Phones>> \textit{IEEE International Conference on Consumer Electronics (ICCE), 2012}

\bibitem{2} \textsc{Rea Mauricio, Cordobés Héctor, Gustiniano Domenico},<<Twins: Time-of-flight based Wireless Indor Navigation System>>

\bibitem{3} \textsc{Bianca Bobescu, Marian Alexandru} <<Mobile indoor positioning using Wifi localization>> Review of the Air Force Academy. Transilvania University, Brasov, Romania

\bibitem{4} \textsc{Mayur Tawari},\textsc{Onkar Pathak},\textsc{Rajesh Palaskar} y \textsc{Rajesh Palkar}, <<Wi-Fi Indoor Positioning System Based on RSSI Measurements from Wi-Fi Access Points –A Tri-lateration Approach>>, \textit{International Journal of Scientific \& Engineering Research. V5}, 2014.

\bibitem{5} \textsc{C. Yang and H. r. Shao}, <<WiFi-based indoor positioning,>> in IEEE Communications Magazine, vol. 53, no. 3, pp. 150-157, March 2015. doi: 10.1109/MCOM.2015.7060497

\bibitem{6} \textsc{Zahid Farid, Rosdiadee Nordin} y \textsc{Mahamod Ismail}, <<Recent Advances in Wireless Indoor Localization Techniques and System>>, \textit{Journal of Computer Networks and Communications}, 2013.

\bibitem{7} \textsc{Zhao Kai, Li Binghao} y \textsc{Andrew Dempster}, <<A Comparison of algorithms adopted in fingerprinting indoor positioning systems>>, \textit{IGNSS Symposium}, 2013.

\bibitem{8} \textsc{Ma, R., Guo, Q., Hu, C., \& Xue, J.} (2015). <<An Improved WiFi Indoor Positioning Algorithm by Weighted Fusion>>. Sensors.

\bibitem{9} \textsc{Habibi Lashkari, Arash \& Parhizkar, Behrang \& Ng Ah Ngan, Mike.} (2010). <<WIFI-based indoor positioning system>>. Computer and Network Technology, International Conference on. 76-78. 10.1109/ICCNT.2010.33. 

\bibitem{10} \textsc{Zourmand A., Sheng N., Lai Kun A., et al},<<Human Counting and Indoor Positioning System Using WiFi Technology>> , \textit{IEEE, International Conference on Automatic Control and Intelligent Systems.} October 20,2018, Shah Alam, Malaysia.

\bibitem{11} \textsc{Davies K., Jones I.} y \textsc{Shapiro J.},<<A Bayesian Approach to Dealing with Device Heterogeneity in an Indoor Positining System , \textit{International Conference on Indoor Positioning and Indoor Navigation.} September 2018, Nantes, France.

\bibitem{12} \textsc{Le Dortz N, Zetterberg P. & Gain F.}, <<Wifi Fingerpirnt Indoor Positioning System Using Probability Distribution Comparison>>, \textit{IEEE ICASSP 2012}
\bibitem{13} \textsc{Beom-Ju Shin, Kwang-Won Lee, Sun-Ho Choi, et al},<<Indoor WiFi positining System fior Android Based Smartphone>> , \textit{ICTC 2010}

\bibitem{14} \textsc{Lu Y., Zhang D. Cheng Y., et al},<<An Improved Method and Implementation of Indoor Positioning Fingerprint Matching Localization Based on WLAN>>, \textit{Springer Nature},Switzerland AG 2019

\bibitem{15} \textsc{},<<Towards the Implementation of Recurrent Neural Networks Schemes for WiFi Fingerprint-Based Indoor Positioning>> , \textit{IEEE 2018}

\bibitem{16} \textsc{Y Lu et al},<<Implementation of Fingerprint Matching Method for Indoor Position Based on Virtual Reality Technology>>
\end{thebibliography}