\chapter{Referencias}

\begin{thebibliography}{X}
\bibitem{1} \textsc{Zahid Farid, Rosdiadee Nordin} y \textsc{Mahamod Ismail}, <<Recent Advances in Wireless Indoor Localization Techniques and System>>, \textit{Journal of Computer Networks and Communications}, 2013.
\bibitem{2} \textsc{Zhao Kai, Li Binghao} y \textsc{Andrew Dempster}, <<A Comparison of algorithms adopted in fingerprinting indoor positioning systems>>, \textit{IGNSS Symposium}, 2013.
\bibitem{3} \textsc{Mayur Tawari},\textsc{Onkar Pathak},\textsc{Rajesh Palaskar} y \textsc{Rajesh Palkar}, <<Wi-Fi Indoor Positioning System Based on RSSI Measurements from Wi-Fi Access Points –A Tri-lateration Approach>>, \textit{International Journal of Scientific \& Engineering Research. V5}, 2014.
\bibitem{4} \textsc{Habibi Lashkari, Arash \& Parhizkar, Behrang \& Ng Ah Ngan, Mike.} (2010). <<WIFI-based indoor positioning system>>. Computer and Network Technology, International Conference on. 76-78. 10.1109/ICCNT.2010.33. 
\bibitem{5} \textsc{C. Yang and H. r. Shao}, <<WiFi-based indoor positioning,>> in IEEE Communications Magazine, vol. 53, no. 3, pp. 150-157, March 2015. doi: 10.1109/MCOM.2015.7060497
\bibitem{6} \textsc{Chua Ching, Jeleen, Domingo, Carolyn, Iglesia, Kyla, et al.}, <<Mobile Indoor Positioning Using Wi-fi Localization and Image Processing>>, Theory and Practice of Computation (2013) Springer Japan.
\bibitem{7} \textsc{Bianca Bobescu, Marian Alexandru} <<Mobile indoor positioning using Wifi localization>> Review of the Air Force Academy. Transilvania University, Brasov, Romania
\bibitem{8} \textsc{Ma, R., Guo, Q., Hu, C., \& Xue, J.} (2015). <<An Improved WiFi Indoor Positioning Algorithm by Weighted Fusion>>. Sensors.
\bibitem{9} \textsc{Chou, Yun-Chih.} <<Characterizing Wi-Fi Network Discovery.>> 10.13140/RG.2.2.36542.18241.(2017).
\bibitem{10} \textsc{Cunche, Mathieu.} (2013). <<I know your MAC Address: Targeted tracking of individual using Wi-Fi>>. Journal of Computer Virology and Hacking Techniques. 10. 219-227. 10.1007/s11416-013-0196-1. 
\bibitem{11}\textsc{Olivares Camargo, Jose L.} <<Modelo de Cobertura Para redes Inalámbricas de Interiores>>, (2009) Proyecto Fin de Carrera, Departamento de Teoría de la Señal y Comunicaciones. Universidad de Sevilla, Escuela Superior de Ingenieros.\label{pdf:1}
\bibitem{12} \textsc{Soriano Montero, J. C.} 2006. <<Modelo Experimental de Propagación de RF en Espacio Libre y Vegetación a 9.1Ghz.>> Cap.II Pág. 7.
\textit{Tesis Licenciatura. Ingeniería en Electrónica y Comunicaciones.} Departamento de Computación, Electrónica, Física e Innovación, Escuela de Ingeniería y Ciencias, Universidad de las Américas Puebla. \label{pdf:modprop}

\bitem{13} \textsc{Mehmood, Hamid & Tripathi, Nitin & Tipdecho, Taravudh. (2010)}. <<Indoor Positioning System Using Artificial Neural Network>>. \textit{Journal of Computer Science. 6. 10.3844/jcssp.2010.1219.1225.}

\bibitem{14} Accedido en Julio 2018. [En línea]. Disponible en: \url{http://tools.dlink.com/intro/wfp/help} \label{fig:prop}
\bibitem{15} Accedido en Julio 2018. [En línea]. Disponible en: \url{https://goo.gl/esTKaJ} \label{fig:paginaHP}
\bibitem{16} Accedido en Julio 2018. [En línea]. Disponible en: \url{https://goo.gl/kV6KU8}

\end{thebibliography}
